A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Add CTL and Kripke structure descriptions

>>>>

Based upon this two functions and the $\mu$-Calculus, one can now do CTL model
checking by representing a CTL formula $f$ as a $\mu$-Calculus relational term
$R$. Assuming standard CTL syntax and semantics, i.e. for the set of atomic
propositions $AP$
\begin{enumerate}
    \item{$p \in AP$ is a CTL formula.}
    \item{
        Given two CTL formulas $f_1$ and $f_2$, also $\neg f_1$, $f_1 \land f_2$,
        $\text{\textbf{EX}} f$,
        $\text{\textbf{E}} \lbrack f_1 \text{\textbf{U}} f_2 \rbrack$ and
        $\text{\textbf{EG}} f_1$ are CTL formulas.
    }
\end{enumerate}

A CTL formula is represented by a \textit{Kripke structure} \newline
$\mathcal{M} \left( \mathcal{S}, \mathcal{S}_0, R, L \right)$, where $\mathcal{S}$
is a finite set of states over $AP$, $\mathcal{S}_0 \in \mathcal{S}$ is the set
of initial states, $R \subseteq \mathcal{S} \times \mathcal{S}$ is the transition
relation and $L: \mathcal{S} \rightarrow 2^{AP}$ is a labelling function. An
infinite sequence of states $\pi = s_0s_1s_2\ldots$ is called \textit{path} if
$\forall i \in \mathbb{N}.\left( s_i, s_{i+1} \right) \in R$.
